---
title: "Chick Project Example"
subtitle: 'MSc in Statistics 2025/26, Imperial College London'
author: "Arden Temple-Bowles"
format:
  html:
    toc: true
    highlight: tango
    self-contained: true
    df-print: paged
  pdf: default
format-links: false
bibliography: "chick-ref.bib" 
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>

```{r setup, include = FALSE, tidy=TRUE}
#######################
# Set up
#######################

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
include_solutions <- TRUE
```
```{r setup2, include=FALSE, tidy=TRUE}
require(rmarkdown)
require(knitr)
require(kableExtra)
# Put any library imports and other preamble here.
```

# Introduction
In this document we provide examples of what might be included in a coursework document. It also provides good examples of referencing, including tables and figures and bibliography. It also includes a code appendix, such that the code for graphs does not need to be shown everywhere @box1964analysis. 

# Chick Weight over Time {#weight-by-time}
``` {r}
#######################
# Setting up chick weight
#######################

#setting up the chick data
chicks <- ChickWeight
```
The chick dataset contains information on their weight over time, and the diet and chick number. 

```{r echo = F}
#| layout-ncol: 2
#| label: fig-distribution-plots
#| fig-cap: "Two example plots relating to the chick weight"
#| fig-subcap: 
#|   - "Chick weight over time."
#|   - "Chick weight by diet"

#Plotting chick weight over time
plot(x = chicks$Time, 
     y = chicks$weight,
     ylab = "Chick Weight (g)", 
     xlab = "Time",
    col = factor(chicks$Diet))

#Plotting chick weight by diet
plot(x = chicks$Diet, 
     y = chicks$weight,
     ylab = "Chick Weight (g)", 
     xlab = "Diet",
    col = c(1:4))
```




```{r echo = F}
#| label: fig-weight-time
#| fig-cap: "Scatter plot of chick weight over time."
plot(x = chicks$Time, 
     y = chicks$weight,
     ylab = "Chick Weight (g)", 
     xlab = "Time",
    col = factor(chicks$Diet))
```

```{r echo = F}
#| label: fig-weight-diet
#| fig-cap: "Scatter plot of chick weight by diet."

#Plotting chick weight over time
plot(x = chicks$Diet, 
     y = chicks$weight,
     ylab = "Chick Weight (g)", 
     xlab = "Diet",
    col = c(1:4))
```

How many chicks data do we have on each day? 
```{r echo = FALSE}
#| label: tbl-day-count
#| tbl-cap: "Table of chick numbers by day."
day_counts <- table(chicks$Time)
knitr::kable(day_counts, col.names = c("Day", "Count"))
```

How many chicks data do we have on each diet? 
```{r echo=FALSE}
#| label: tbl-diet-count
#| tbl-cap: "Table of chick numbers by diet"
day_counts <- table(chicks$Diet)
knitr::kable(day_counts, col.names = c("Diet", "Count"))
```

```{r}
# fit linear model
weight_lm <- lm(formula = weight ~ 1 + Diet, chicks)

# extract coefficients and standard errors
mass_lm_coefficients <- summary(weight_lm)$coefficients[,1:2]
mass_lm_coefficients
```

# Code appendix

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```

# References
