---
title: "Chick Project Example"
subtitle: 'MSc in Statistics 2025/26, Imperial College London'
author: "Arden Temple-Bowles"
format:
  html:
    toc: true
    highlight: tango
    self-contained: true
    df-print: paged
  pdf: default
format-links: false
bibliography: "chick-ref.bib" 
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>

```{r setup, include = FALSE, tidy=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
include_solutions <- TRUE
```
```{r setup2, include=FALSE, tidy=TRUE}
require(rmarkdown)
require(knitr)
require(kableExtra)
# Put any library imports and other preamble here.
```

# Introduction
In this document we provide examples of what might be included in a coursework document. It also provides good examples of referencing, including tables and figures and bibliography. It also includes a code appendix, such that the code for graphs does not need to be shown everywhere. 

# Chicks
``` {r}
#setting up the chick data
chicks <- ChickWeight
```



# Code appendix

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```

# References
